Algebraic File Synchronization: Adequacy and Completeness

### 2017-10-19 p2/ordering.tex
Added TODO comments

The principal ideas behind these conditions are 
\cref{ax_separate_commute}, from which we know that commands on incomparable
nodes can be applied in any order, so we only need to focus on the order of commands
with comparable nodes;
\cref{connected_changes}, from which we know that if $U$ contains commands on two comparable
nodes, then it contains commands on all nodes in between, so it is enough to specify
the order of commands on directly related nodes;
and finally, \cref{ax_directchild_breaks,ax_directparent_breaks}, from which we know
that commands on parent--child pairs must be construction or destruction pairs.
Investigating these pairs we see that they are identified by the output value of the first command ($y$),
which in turn determines whether the command on the parent or the child must precede the other.

@@

\begin{mylem}\mlabel{simple_distant_pairs}
For any simple sequence $\wrksx{S}$,
if $\cxynv\cc\czwmv$ is a subsequence of $S$ and $n=\parent(m)$ or $\parent(n)=m$,
then $\cxynv\cc\czwmv$ is either a construction or a destruction pair.
\end{mylem}
\begin{proof}
Informally speaking, the proposition means that
the two commands must form a construction or destruction pair even
if they are not next to each other.
This is true because in simple sequences
there cannot be another command on $n$ or $m$,
so if the commands are incompatible, no command between them can change that.
In fact, this \namecref{simple_distant_pairs} is the general case
of \cref{ax_directchild_breaks,ax_directparent_breaks}.

% BACK_TO_THE_FS TODO
% TODO Review any proof depending on "nothing changes FS at n until...".
% TODO Move to rules
% TODO APPENDIX
Formally, we prove our proposition by contradiction,
and in this version of the proof we reach back to our filesystem model.
We assume $\wrks{S}$ and therefore there is a $\FS$ for which $S\aFS\neq\fsbroken$,
but $S$ contains commands on a node and its parent that do not form a construction or destruction pair.
Select two such commands, $\cxynv$ and $\czwmv$,
and split $S$ around them into three parts:
\[ S = S_0 \cc \cxynv \cc S_1 \cc \czwmv \cc S_2. \]
As $S$ is simple, there cannot be any commands on $n$ or $m$ in $S_1$,
and therefore $(S_0\cc\cxynv\cc S_1)\FS(n) = y$,
and $[(S_0\cc\cxynv\cc S_1)\FS(m)] = [S_0\FS(m)]$.
If $[z]\neq[S_0\FS(m)]$, then $S\aFS=\fsbroken$, which is a contradiction.

>>>>

The principal ideas behind these conditions are 
\cref{ax_separate_commute}, from which we know that commands on incomparable
nodes can be applied in any order, so we only need to focus on the order of commands
with comparable nodes;
\cref{connected_changes}, from which we know that if $U$ contains commands on two comparable
nodes, then it contains commands on all nodes in between, so it is enough to specify
the order of commands on directly related nodes;
and finally, \cref{simple_distant_pairs}, from which we know
that commands on parent--child pairs must be construction or destruction pairs.
Investigating these pairs we see that they are identified by the output value of the first command ($y$),
which in turn determines whether the command on the parent or the child must precede the other.

@@

\begin{mylem}\mlabel{simple_distant_pairs}
For any simple sequence $\wrksx{S}$,
if $\cxynv\cc\czwmv$ is a subsequence of $S$ and $n=\parent(m)$ or $\parent(n)=m$,
then $\cxynv\cc\czwmv$ is either a construction or a destruction pair.
\end{mylem}

Informally speaking, the proposition means that
the two commands must form a construction or destruction pair even
if they are not next to each other.
This is true because in simple sequences
there cannot be another command on $n$ or $m$,
so if the commands are incompatible, no command between them can change that.
In fact, this \namecref{simple_distant_pairs} is the general case
of \cref{ax_directchild_breaks,ax_directparent_breaks}.

TODO MOVE TO AMONG THE AXIOMS TO AVOID DUPLICATION.
BUT THIS NEEDS THE DEFINITION OF SIMPLE SEQUENCES.

\begin{proof}
% BACK_TO_THE_FS TODO
% TODO APPENDIX
Formally, we prove our proposition by contradiction,
and in this version of the proof we reach back to our filesystem model.
We assume $\wrks{S}$ and therefore there is a $\FS$ for which $S\aFS\neq\fsbroken$,
but $S$ contains commands on a node and its parent that do not form a construction or destruction pair.
Select two such commands, $\cxynv$ and $\czwmv$,
and split $S$ around them into three parts:
\[ S = S_0 \cc \cxynv \cc S_1 \cc \czwmv \cc S_2. \]
As $S$ is simple, there cannot be any commands on $n$ or $m$ in $S_1$,
and therefore $(S_0\cc\cxynv\cc S_1)\FS(n) = y$,
and $[(S_0\cc\cxynv\cc S_1)\FS(m)] = [S_0\FS(m)]$.
If $[z]\neq[S_0\FS(m)]$, then $S\aFS=\fsbroken$, which is a contradiction.

### 2017-10-19 p2/rec-intro.tex
Added TODO comments

\begin{mydef}[Reconciliation]\label{def:reconciliation}
We determine $\reca$---which we apply to $\FS_B$ 
to reconcile it with $\FS_A$---to be
the largest subset of $A\setminus B$
that is independent of $B\setminus A$,
where $A$ and $B$ are simple sequences representing
the updates applied to replicas $\FS_A$ and $\FS_B$:
\[ \reca = \ords{\alpha \whr \alpha\in \ambnp  \ \wedge\   \alpha\indep \bmanp }. \]
\end{mydef}

>>>>

\begin{mydef}[Reconciliation]\mlabel{def:reconciliation}
We determine $\reca$---which we apply to $\FS_B$ 
to reconcile it with $\FS_A$---to be
the largest subset of $A\setminus B$
that is independent of $B\setminus A$,
where $A$ and $B$ are simple sequences representing
the updates applied to $\FS$ to arrive at replicas $\FS_A$ and $\FS_B$:
\[ \reca = \ords{\alpha \whr \alpha\in \ambnp  \ \wedge\   \alpha\indep \bmanp }. \]
\end{mydef}
